Abstract Data Type Inference

### 2015-03-07 inference.tex
Defined symbolic ADT inference problem.

For the remainder of this work, we assume each set of executions $E$ comes
equipped with a matching scheme $M$, and abbreviate $H(M,E)$ by $H(E)$.

@@

TODO DEFINE THE ADT INFERENCE PROBLEM

>>>>

For the remainder of this work, we assume each set of executions $E$ comes
equipped with a faithful matching scheme $M$, and abbreviate $H(M,E)$ by $H(E)$.

@@

TODO DEFINE HISTORY LOGIC

The \emph{symbolic ADT inference problem} is to compute a first-order history
formula $F$ for a given ADT $A$ such that
\begin{itemize}

  \item $h \models F$ for all $h \in \ker A$, and

  \item $h \not\models F$ for all $h \in B$,

\end{itemize}
where $B$ is the complement of $\ker A$.
